\documentclass[letterpaper,10pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
%\usepackage[numbers]{natbib}
%\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\usepackage[spanish]{babel}
\usepackage{hyperref}
%\usepackage{tex4ht} % activate when creating an HTML

\title{Identificación Inicial de Fuentes de Información}

\author{Alexander Enrique Urieles Nieto\\
\href{mailto:aeurielesn@gmail.com}{\nolinkurl{aeurielesn@unal.edu.co}}}

\date{Maestría en Sistemas y Computación\\
Departamento de Ingeniería de Sistemas e Industrial\\
Universidad Nacional de Colombia}

\begin{document}

\maketitle

\section*{Identificación inicial de fuentes de información}

A continuación se presenta una lista inicial de fuentes de información
donde artículos teóricos y experimentales afines a \emph{Stringology} y 
la compresión de texto han sido publicados a través de los años.

Los vínculos de cada conferencias enlazan a las páginas del año en curso
o a la conferencia más reciente.

\subsection*{Revistas}

\begin{itemize}

%15
\item[1.] \textbf{SIAM Journal on Scientific Computing (SISC)}

%The SIAM Journal on Scientific Computing contains research articles on numerical methods and techniques for scientific computation. Papers address computational issues relevant to the solution of scientific or engineering problems and generally include computational results demonstrating the effectiveness of the proposed techniques.

SISC contiene numerosos artículos de investigación en métodos numéricos y
técnicas para computación científica con interés en solución de problemas científicos
e ingenieriles, y generalmente incluyen resultados computaciones demostrando la
efectividad de las técnicas propuestas.

Homepage: \url{http://www.siam.org/journals/sisc.php}

%16
\item[2.] \textbf{Journal of the ACM (JACM)}

%The Journal of the ACM (JACM) provides coverage of the most significant work going on in computer science, broadly construed. It is a peer-reviewed journal, published six times a year by ACM.
%We publish original research papers of lasting value in computer science. To be accepted, a paper must be judged to be truly outstanding in its field and to be of interest to a wide audience. We are particularly interested in work at the boundaries, both the boundaries of subdisciplines of computer science and the boundaries between computer science and other fields.

JACM provee abarca los trabajos más significativos relevantes para ciencias
de la computación, artículos de investigación originales y de interés 
para una audiencia amplia.

Homepage: \url{http://jacm.acm.org/}

%17
\item[3.] \textbf{Discrete Mathematics, Algorithms and Applications (DMAA)}

%The aim of this journal is to advance and promote the theory and applications of discrete mathematics, which is a research area in mathematics with applications in computer science, industrial engineering, bio-informatics, chemistry and communication networks.

DMAA busca avanzar y promover la teoría y aplicaciones de las matemáticas discretas.

Matemáticas discretas es un área de investigación con aplicaciones en ciencias de la
computación, ingeniería industrial, bioinformática, química y redes de comunicación. 

Homepage: \url{http://www.worldscinet.com/dmaa/dmaa.shtml}


%18
\item[4.] \textbf{ACM Transactions on Information Systems (TOIS)}

%ACM Transactions on Information Systems (TOIS) is a scholarly journal that publishes the highest quality papers about the design and evaluation of computer software that helps people find, organize, analyze, and use information in a variety of media.  TOIS is published quarterly.

TOIST es una revista académica que publica los artículos de mayor calidad teniendo en cuenta
el diseño y evaluación del software que ayuda a las personas a encontrar, organizar, analizar, y
usar información en una gran variedad de medios.

Homepage: \url{http://tois.acm.org/}

%19
\item[5.] \textbf{Journal of Discrete Algorithms (JDA)}

Homepage: {\small \url{http://www.sciencedirect.com/science/journal/15708667}}

%20
\item[6.] \textbf{Algorithmica}

Homepage: {\small \url{http://springerlink.metapress.com/content/0178-4617/}}

\end{itemize}

\subsection*{Conferencias}

\begin{itemize}

%1
\item[7.] \textbf{ACM-SIAM Annual Symposium on Discrete Algorithms (SODA)}

Se enfoca en tópicos de investigación relacionados a algoritmos eficientes
y estructuras de información para el campo de problemas discretos.

Homepage: \url{http://www.siam.org/meetings/da11/}

%2
\item[8.] \textbf{Data Compression Conference (DCC)}

Es un foro internacional con interés en trabajos teóricos y experimentales
que se están desarrollando actualmente con respecto a la compresión de
información y aplicaciones afines.

Homepage: \url{http://pages.cs.brandeis.edu/~dcc/}

%3
\item[9.] \textbf{Annual Symposium on Combinatorial Pattern Matching (CPM)}

CPM tiene interés en derivar propiedades combinatorias no triviales para 
estructuras complicadas tales como árboles, expresiones regulares, grafos, conjuntos
de puntos, entre otros; y explotarlas para lograr mejorar el rendimiento
para el problema computacional correspondiente.

Homepage: \url{http://cpm2011.unipa.it/}

%4 -> IWOCA
\item[10.] \textbf{Australasian Workshop on Combinatorial Algorithms (AWOCA)}

Tenía interés en artículos originales e investigaciones no publicadas orientadas
a problemas y un énfasis en discusiones informales en áreas como Algoritmia y
Estructuras de Datos, Teoría de la Complejidad, Criptografía, \emph{Stringology},
entre otros.

Homepage: \url{http://www.ballarat.edu.au/conferences/awoca2006/}

%5
\item[11.] \textbf{International Workshop on Combinatorial Algorithms (IWOCA)}

Anteriormente AWOCA.

Homepage: \url{http://www.iwoca.org/}

%6
\item[12.] \textbf{ACM Symposium on Theory of Computing (STOC)}

%Papers presenting original research on theoretical aspects of computer science are sought. Typical, but not exclusive, topics of interest include algorithmic graph theory, algorithms and data structures, applications of logic, biological computing, computational biology, complexity theory, cryptography, computational algebra, computational geometry, machine learning, parallel and distributed computation, and probabilistic computation.

STOC tiene como interés artículos de investigación originales en aspectos
teóricos de la ciencia de la computación tales como algoritmia y estructuras de 
información, teoría de grafos, aplicaciones de lógica, computación biológica,
criptografía, entre otros.

Homepage: \url{http://www.sigact.org/stoc.html}

%7 -> SPIRE
\item[13.] \textbf{South American Workshop on String Processing (WSP)}

%WSP'97 covers research in all aspects of String Processing. Typical topics of interest include: dictionary algorithms, text searching, pattern alignment, DNA sequencing and applications in molecular biology, voice or natural language processing. Surveys of important results are also invited.

WSP cubre tópicos de investigación en todos los aspectos de procesamiento
de cadenas tales como algoritmos de diccionario, búsquedas de texto,
alineamiento de patrones, sequencias de DNA, procesamiento del lenguaje
natural, entre otros.

Homepage: \url{http://sunsite.dcc.uchile.cl/~sccc/wsp97/wsp97.html}

%8
\item[14.] \textbf{International Symposium on String Processing and Information Retrieval (SPIRE)}

%The scope of the SPIRE series of symposia includes not only fundamental algorithms in string processing and information retrieval, but also SP and IR techniques as applied to areas such as computational biology, DNA sequencing, and Web mining. Given its interdisciplinary nature, SPIRE offers a unique opportunity for researchers from these different areas to meet and network.

Anteriormente WSP.

Homepage: \url{http://spire2011.isti.cnr.it/}

%9
\item[15.] \textbf{ACS/IEEE International Conference on Computer Systems and Applications (AICCSA)}

Es un foro para científicos e ingenieros para intercambiar y diseminar los últimos adelantos
en tecnologías de la información.

Homepage: \url{http://www.aiccsa.org/}

%10
\item[16.] \textbf{International Conference on Current Trends in Theory and Practice of Computer Science (SOFSEM)}

Es una conferencia dedicada a la teoría y práctica de la ciencia de la computación.

Homepage: \url{http://sofsem.cz/}

%11
\item[17.] \textbf{Prague Stringology Conference (PSC)}

%It is an international conference focusing on stringology and related areas. It is organized annually by the Prague Stringology Club, a research group in the Department of Theoretical Computer Science at the Faculty of Information Technology of Czech Technical University in Prague. The proceedings of recent conferences are indexed in DBLP.

PSC es una conferencia internacional enfocada en \emph{Stringology} y áreas afines.

Homepage: \url{http://www.stringology.org/event/2010/}

%12
\item[18.] \textbf{Annual International Computing and Combinatorics Conference (COCOON)}

Homepage: \url{http://theory.utdallas.edu/COCOON11/}

\pagebreak

%13
\item[19.] \textbf{Annual IEEE Symposium on Foundations of Computer Science (FOCS)}

%Papers presenting new and original research on theory of computation are sought. Typical but not exclusive topics of interest include: algorithms and data structures, computational complexity, cryptography, privacy, computational geometry, computational game theory, algorithmic graph theory and combinatorics, optimization, randomness in computing, parallel and distributed computing, machine learning, applications of logic, algorithmic algebra and coding theory, theoretical aspects of databases, information retrieval, networks, computational biology, robotics, and quantum computing.

FOCS tiene interés en artículos de investigación nuevos y originales en teoría
de la computación tales como algoritmos y estructuras de información,
complejidad computacional, criptografía, privacidad, geometría computacional,
entre otros.

Homepage: \url{http://www.cs.ucla.edu/~rafail/FOCS11/}

%14
\item[20.] \textbf{Symposium on Mathematical Foundations of Computer Science (MFCS)}

%The MFCS symposia encourage high-quality research in all branches of theoretical computer science. Their broad scope provides an opportunity to bring together researchers who do not usually meet at specialized conferences.

MFCS tiene interés en artículos de investigación de alta calidad en todas las áreas
de la ciencia de la computación teórica.

Homepage: \url{http://mfcs.mimuw.edu.pl/}

\end{itemize}


\end{document}
